% Synchronized to r30467
\begin{tabular}{rlcl}
  Opt and Docs: & 07. Januar 2008 & Frank Saurbier & \altlink{mailto:c3surf@arcor.de}\\
  Tex-Docs: & 01. April 2009 & Helmut Backhaus & \altlink{mailto:helmut.backhaus@gmx.de}\\
  Handover: & 01. Mai 2010 & fli4l-Team & \altlink{mailto:team@fli4l.de}\\
\end{tabular}


\section{Hints Concerning Other Opts}

\subsection{cpmvrmlog Config}

\marklabel{C3SURFLOG}{ }
\underline{Example For The C3SURF Log Directory, With mini\_httpd Restart}
\begin{example}
\begin{verbatim}
# archive C3SURF log dir
# once in a month on the 1.st at 01:30
# keep a maximum of 12 archives
CPMVRMLOG_n_ACTION='move'
CPMVRMLOG_n_SOURCE='/var/log/c3surf/c3surf_*.log'
CPMVRMLOG_n_DESTINATION='/data/Archive/log/c3surf'
CPMVRMLOG_n_CUSTOM='/usr/local/bin/c3surf_kill_httpd.sh'
CPMVRMLOG_n_MAXCOUNT='12'
CPMVRMLOG_n_CRONTIME='30 1 1 * *'
\end{verbatim}
\end{example}

\subsection{Allow Samba Without Login}

\underline{Use opt\_usercmd with the following entries.}

\begin{example}
\begin{verbatim}
USERCMD_BOOT_N='3'
USERCMD_BOOT_1='/sbin/iptables -I c3surf\_control 1 -v -p udp --dport 
                137:138 -j RETURN' # samba thru c3surf
USERCMD_BOOT_2='/sbin/iptables -I c3surf\_control 1 -v -p tcp --dport
                455 -j RETURN'     # samba thru c3surf
USERCMD_BOOT_3='/sbin/iptables -I c3surf\_control 1 -v -p tcp --dport
                139 -j RETURN'     # samba thru c3surf
\end{verbatim}
\end{example}
By adding the option \var{-d IPsambaHOST} the rules may be
enhanced to reflect the target PC.
\parskip 12pt

Samba ports will pass the Forward-Chain and are not blocked by C3SURF.
If the Forward-Chain denies samba forwards these entries will not change
anything stated there.

The settings in base.txt supersede these settings.

\subsection{Migration From Previous Versions}

\item Migration to Version 2.3.1 (from 2.3.0)
     \begin{itemize}
     \item New variables, only optional. The new range is marked in config.txt like this
     \item ``\# $+$ new 2.3.1 $+$ begin ------------------ delete this line''.
     \item The voucher format has changed, old voucher may still be used,
           but will not be recognized when generating new ones.
           To tidy up, delete all vouchers and generate new ones.
     \end{itemize}

\item Migration to Version 2.3.0 (from 2.2.2)
    \begin{itemize}
    \item If not using vouchers no changes are needed.
    \item New variables for OPT\_C3SURF\_VOUCHER, if vouchers should be used.
    \item The new range is marked in config.txt like this
    \item ``\# $+$ new 2.3.0 $+$ begin ------------------ delete this line''.
\end{itemize}

\item Migration to Version 2.2.2 (from 2.2.1)
    \begin{itemize}
    \item New variables. The new range is marked in config.txt like this
    \item ``\# $+$ new 2.2.2 $+$ begin ------------------ delete this line''.
    \item C3SURF\_CONTROL\_SQUID: optional to control squid, temporary as squid does not follow fli4l's conventions.
    \item Variables for overwriting Quota-Defaults with LOGINUSR\_ACCOUNT are now optional
\end{itemize}

\item Migration to Version 2.2.1 (from 2.2.0)
\begin{itemize}
   \item New variables. The new range is marked in config.txt like this
   \item ``\# $+$ new 2.2.1 $+$ begin ------------------ delete this line''.
   \item C3SURF\_WORKON\_TMP: recommendation for harddisk idle mode 'yes' else 'no' also with FLASH.
   \item C3SURF\_SAVE\_QUOTA: recommendation 'yes'.
\end{itemize}


\item Migration to Version 2.2.0 (from 2.1.0)
\begin{itemize}
   \item New variable ``C3SURF\_CHECK\_ARP'' in config
   (recommendation: 'yes'). It is marked in config.txt like this
   \item ``\# $+$ new 2.2.0 $+$ begin ------------------ delete this line''.
\end{itemize}


\item Migration to Version 2.1.0 (from earlier versions)
\begin{itemize} 
   \item New variables. The new range is marked in config.txt like this
   \item ``\# $+$ new 2.1.0 $+$ begin ------------------ delete this line''.
   \item The MAC-Blackliste (if existing) has to copied to the directory\\
   ``C3SURF\_PERSISTENT\_PATH'' manually.
   \item The format of c3surf\_login.log has been expanded by a row.
   Save old logs and delete them in C3SURF\_LOG\_PATH.
\end{itemize}
\end{itemize}
