% Synchronized to r30494
Provides a login registration for users. It is no longer possible for everybody
to use the Internet services of the router freely. Switching of operation modes
is technically possible but not currently implemented.

\wichtig{This is no true user login, the software substitutes
each user to a computer address. When the timeout is reached
the user will be blocked, not the PC (IP address).}

\section{Configuration Of OPT\_LOGINUSER For C3SURF}

\begin{description}
\config {OPT\_LOGINUSR}{OPT\_LOGINUSR}{OPTLOGINUSR}

  Default Setting: \var{OPT\_LOGINUSR}='no'

  OPT\_LOGINUSR='yes': use true login (recommended)

  LOGINUSR provides a true login (User/Password). Account management is done
  in the config file, passwords will be transferred only encrypted.

\config {LOGINUSR\_DELETE\_PERSISTENT\_DATA}{LOGINUSR\_DELETE\_PERSISTENT\_DATA}{LOGINUSRDELETEPERSISTENTDATA}\ \\
  Default Setting: \var{LOGINUSR\_DELETE\_PERSISTENT\_DATA='no'}

  LOGINUSR\_DELETE\_PERSISTENT\_DATA\\
  User data on a harddisk will survive reboots.
  The deault setting 'no' only preserves Account data.

  \achtung{With specifying 'yes' here all user accounts will be deleted on every reboot.
  Afterwards they will be recreated as described below.}

  It is recommended to keep the 'no' here to preserve all account data, i.e.:

\begin{itemize}
\item User Accounts
\item Quotas, if \jump{C3SURFSAVEQUOTA}{\var{C3SURF\_SAVE\_QUOTA='yes'}} is set
(see above) (for defined accounts see: \jump{LOGINUSRACCOUNTxOVERWRITE}{\var{LOGINUSR\_ACCOUNT\_x\_OVERWRITE}})
\end{itemize}

\config {LOGINUSR\_ACCOUNT\_N}{LOGINUSR\_ACCOUNT\_N}{LOGINUSRACCOUNTN}

 \var{LOGINUSR\_ACCOUNT\_N='0'}

  LOGINUSR\_ACCOUNT\_N\\
  The number of accounts defined.\\

\config {LOGINUSR\_ACCOUNT\_x\_USER}{LOGINUSR\_ACCOUNT\_x\_USER}{LOGINUSRACCOUNTxUSER}

   \var{LOGINUSR\_ACCOUNT\_x\_USER='user1'}

  LOGINUSR\_ACCOUNT\_x\_USER\\
  Username for login (mandatory).

\config {LOGINUSR\_ACCOUNT\_x\_PWD}{LOGINUSR\_ACCOUNT\_x\_PWD}{LOGINUSRACCOUNTxPWD}

   \var{LOGINUSR\_ACCOUNT\_x\_PWD='user1\_secret'}

  LOGINUSR\_ACCOUNT\_x\_PWD\\
  Password for login (mandatory)

\config {LOGINUSR\_ACCOUNT\_x\_FORENAME}{LOGINUSR\_ACCOUNT\_x\_FORENAME}{LOGINUSRACCOUNTxFORENAME}

   \var{LOGINUSR\_ACCOUNT\_x\_FORENAME='Vorname'}

  LOGINUSR\_ACCOUNT\_x\_FORENAME\\
  First name of the user for better management (optional, may be empty).
  The content is shown in the logs and in the Admin interface to help the Admin
  to better recognize users being online at the moment.

\config {LOGINUSR\_ACCOUNT\_x\_SURNAME}{LOGINUSR\_ACCOUNT\_x\_SURNAME}{LOGINUSRACCOUNTxSURNAME}

   \var{LOGINUSR\_ACCOUNT\_x\_SURNAME='Nachname'}

  LOGINUSR\_ACCOUNT\_x\_SURNAME\\
  Last name of the user for better management (optional, may be empty).
  The content is shown in the logs and in the Admin interface to help the Admin
  to better recognize users being online at the moment.

\config {LOGINUSR\_ACCOUNT\_x\_EMAIL}{LOGINUSR\_ACCOUNT\_x\_EMAIL}{LOGINUSRACCOUNTxEMAIL}

   \var{LOGINUSR\_ACCOUNT\_x\_EMAIL='usr1@home.de'}

  LOGINUSR\_ACCOUNT\_x\_EMAIL\\
  E-Mail of the user for better management (optional, may be empty).
  The content is shown in the logs and in the Admin interface to help the Admin
  to better recognize users being online at the moment.

\config {LOGINUSR\_ACCOUNT\_x\_OVERWRITE}{LOGINUSR\_ACCOUNT\_x\_OVERWRITE}{LOGINUSRACCOUNTxOVERWRITE}

   \var{LOGINUSR\_ACCOUNT\_x\_OVERWRITE='yes'}

  Optional:LOGINUSR\_ACCOUNT\_x\_OVERWRITE\\
  Overwrite persistent user data on system restart.

  A directoy for persistent data storing may be specified here to hold account data.
  This way the data is preserved after a reboot. With this option
  user accounts and all data for them (statistics) may be overwritten.
\end{description}

\subsection {Optional Parameters For OPT\_LOGINUSR}

\begin{description}

\config {LOGINUSR\_ACCOUNT\_x\_TIME}{LOGINUSR\_ACCOUNT\_x\_TIME}{LOGINUSRACCOUNTxTIME}

   \var{LOGINUSR\_ACCOUNT\_x\_TIME='60'}

  Time amount solely for this user, defined in minutes.

  If omitted, \jump{C3SURFTIME}{\var{C3SURF\_TIME}} is valid.
  Overwriting only makes sense if \jump{C3SURFQUOTA}{\var{C3SURF\_QUOTA='yes'}} has been defined.

\config {LOGINUSR\_ACCOUNT\_x\_BLOCKTIME}{LOGINUSR\_ACCOUNT\_x\_BLOCKTIME}{LOGINUSRACCOUNTxBLOCKTIME}

   \var{LOGINUSR\_ACCOUNT\_x\_BLOCKTIME='240'}

  Locking time solely for this user.

  If omitted, \jump{C3SURFBLOCKTIME}{\var{C3SURF\_BLOCKTIME}} is valid.
  Overwriting only makes sense if
  \jump{C3SURFQUOTA}{\var{C3SURF\_QUOTA='yes'}} has been defined.

\config {LOGINUSR\_ACCOUNT\_x\_COUNTER}{LOGINUSR\_ACCOUNT\_x\_COUNTER}{LOGINUSRACCOUNTxCOUNTER}

   \var{LOGINUSR\_ACCOUNT\_x\_COUNTER='1'}

  Number of logins solely for this user.

  If omitted, \jump{C3SURFCOUNTER}{\var{C3SURF\_COUNTER}} is valid.
  Overwriting only makes sense if
  \jump{C3SURFQUOTA}{\var{C3SURF\_QUOTA='yes'}} has been defined.

\config {LOGINUSR\_ACCOUNT\_x\_CURFEW}{LOGINUSR\_ACCOUNT\_x\_CURFEW}{LOGINUSRACCOUNTxCURFEW}

   \var{LOGINUSR\_ACCOUNT\_x\_CURFEW='List of curfews'}

   Format: (List of curfews 0-23 separated by spaces)
  \begin{example}
  \begin{verbatim}
  Example: LOGINUSR_ACCOUNT_x_CURFEW='0 1 2 3 4 5 6 7 21 22 23'
  \end{verbatim}
  \end{example}
  Meaning: A login is allowed only between 8:00-20:59. The login will always be denied if the user tries
  to login within the hour in the list (plus 0-59 minutes).

  If the user is logged in and runs into a curfew, he will be logged out without a warning.
  The logout behavior can be prevented by specifying \jump{C3SURFCHECKCURFEW}
  {\var{C3SURF\_CHECK\_CURFEW}}='no'.

  By using this list access can be restricted very flexible. The list can also be managed in the
  Web interface. No checking of the list is performed. \achtung{Only the numbers from 0 to 23 make sense!}

  OPT\_C3SURF Parameters belonging here:\\
  \jump{C3SURFCHECKCURFEW}{\var{C3SURF\_CHECK\_CURFEW}}='no'
    \begin{itemize}
        \item{C3SURF\_CHECK\_CURFEW='no'}: no automatic logout when reaching curfews is performed.
        \item{C3SURF\_CHECK\_CURFEW='yes'} (Standard): users will be logged out automatically when reaching curfews.
    \end{itemize}
\end{description}
