% Synchronized to r30831
\subsection{Warning}
\wichtig{Without \jump{OPTLOGINUSR}{\var{OPT\_LOGINUSR='yes'}} any person
with an IP address assigned to their computer by the router (eg from an
open Wi-Fi), has free access to the Internet and unblocked services on
the router. c3Surf is helpful for blocking services, but is no
substitute for a proper configuration of the firewall in base.txt.}

\subsection{Recommendation}
\wichtig{The router should contain a recovery version build. With an improper
configuration you may lock yourself out completely.}

\subsection{Errors}
Error descriptions containing config informations may be posted on the fli4l newsgroups
\altlink{http://www.fli4l.de/hilfe/newsgruppen-forum/}.

\subsection{License}
This software is licensed under the terms of the GNU General Public License
published in version 2 or following. According to it, this software is free
for users, developers and companies. It is good style, to mention the
original developers when further using this piece of software.
This is especially true for public domain works.

\subsection{Literature}
If you like to open your net to others you should concern the legal situation.

A CC licensed work (in german) can be found at:\\
Rechtsfragen offener Netze:\\
\altlink{http://digbib.ubka.uni-karlsruhe.de/volltexte/1000007749}\\
Autor: Mantz, Reto\\
Reihe: Schriften des Zentrums f체r Angewandte Rechtswissenschaft / ZAR\\
Zentrum f체r Angewandte Rechtswissenschaft, Universit채t Karlsruhe (TH)\\
Band: 8\\
Verlag: Universit채tsverlag Karlsruhe\\
ISBN: 978-3-86644-222-1\\
Erschienen: 10.04.2008
