% Synchronized to r29817
\paragraph*{Name}
DS2423 - 4kbit 1-Wire RAM with Counter 
\paragraph*{Synopsis}
RAM and counters.


\textbf{1D} [.]XXXXXXXXXXXX[XX][/[ \textbf{counters.[A$|$B$|$ALL]} $|$ \textbf{memory} $|$ \textbf{pages/page.[0-15$|$ALL]} $|$ \textbf{pages/count.[0-15$|$ALL]}
$|$           \textbf{address} $|$ \textbf{crc8} $|$ \textbf{id} $|$ \textbf{locator} $|$ \textbf{r\_address} $|$ \textbf{r\_id} $|$ \textbf{r\_locator} $|$ \textbf{type}
 ]] 
\paragraph*{Family Code}


\textit{1D} 
\paragraph*{Special Properties}

\subparagraph*{counters.A counters.B counters.ALL}\textit{read-only,}
unsigned integer 

Debounced external counter. Associated with RAM \textit{page.14} and \textit{page.15} Note:
counter increments only. It is reset when the chip loses power. 

\textit{ALL} returns the two values, separated by a comma. They are read sequentially.

\subparagraph*{memory}\textit{read-write,} binary 

512 bytes of memory. 
\subparagraph*{pages/page.0 ... pages/page.15 pages/page.ALL}\textit{read-write,} binary


Memory is split into 16 pages of 32 bytes each. Memory is RAM, contents
are lost when power is lost. \textit{ALL} is an aggregate of the pages. Each page
is accessed sequentially. 
\subparagraph*{pages/count.0 ... pages/count.15 pages/count.ALL}\textit{read-only,}
unsigned integer 

 Write access to each page of memory. Actually only \textit{page.12} and \textit{page.13} have
write counters. 

\textit{page14} and \textit{page.15} 's counters are associated with the external \textit{counters.A}
and \textit{counters.B} triggers. 

The value 0xFFFFFFFF is returned for \textit{pages/count.0} through \textit{pages/count.11}


\textit{ALL} is an aggregate of the counters, comma separated. Each page is accessed
sequentially. 
\paragraph*{Standard Properties}
          
\subparagraph*{address}
\subparagraph*{r\_address}\textit{read-only,} ascii


The entire 64-bit unique ID. Given as upper case hexidecimal digits (0-9A-F).


\textit{address} starts with the \textit{family} code 

\textit{r} address is the \textit{address} in reverse order, which is often used in other
applications and labeling. 
\subparagraph*{crc8}\textit{read-only,} ascii 

The 8-bit error correction portion. Uses cyclic redundancy check. Computed
from the preceding 56 bits of the unique ID number. Given as upper case
hexidecimal digits (0-9A-F). 
\subparagraph*{family}\textit{read-only,} ascii 

The 8-bit family code. Unique to each \textit{type} of device. Given as upper case
hexidecimal digits (0-9A-F). 
\subparagraph*{id}
\subparagraph*{r\_id}\textit{read-only,} ascii 

The 48-bit middle portion of the unique ID number. Does not include the family
code or CRC. Given as upper case hexidecimal digits (0-9A-F). 

\textit{r} id is the \textit{id} in reverse order, which is often used in other applications
and labeling. 
\subparagraph*{locator}
\subparagraph*{r\_locator}\textit{read-only,} ascii 

Uses an extension of the 1-wire design from iButtonLink company that associated
1-wire physical connections with a unique 1-wire code. If the connection is
behind a \textbf{Link Locator} the \textit{locator} will show a unique 8-byte number (16 character
hexidecimal) starting with family code FE. 

If no \textbf{Link Locator} is between the device and the master, the \textit{locator} field
will be all FF. 

\textit{r} locator is the \textit{locator} in reverse order. 
\subparagraph*{present (DEPRECATED)}\textit{read-only,}
yes-no 

Is the device currently \textit{present} on the 1-wire bus? 
\subparagraph*{type}\textit{read-only,} ascii 

Part name assigned by Dallas Semi. E.g. \textit{DS2401} Alternative packaging (iButton
vs chip) will not be distiguished.  
\paragraph*{Alarms}
None. 
\paragraph*{Description}
          
\subparagraph*{1-Wire}\textit{1-wire}
 is a wiring protocol and series of devices designed and manufactured by
Dallas Semiconductor, Inc. The bus is a low-power low-speed low-connector scheme
where the data line can also provide power. 

Each device is uniquely and
unalterably numbered during manufacture. There are a wide variety of devices,
including memory, sensors (humidity, temperature, voltage, contact, current),
switches, timers and data loggers. More complex devices (like thermocouple
sensors) can be built with these basic devices. There are also 1-wire devices
that have encryption included. 

The 1-wire scheme uses a single  \textit{bus} master
and multiple \textit{slaves} on the same wire. The bus master initiates all communication.
The slaves can be  individually discovered and addressed using their unique
ID. 

Bus masters come in a variety of configurations including serial, parallel,
i2c, network or USB adapters. 
\subparagraph*{OWFS design}\textit{OWFS} is a suite of programs that
designed to make the 1-wire bus and its devices easily accessible. The underlying
priciple is to create a virtual filesystem, with the unique ID being the
directory, and the individual properties of the device are represented
as simple files that can be read and written. 

Details of the individual
slave or master design are hidden behind a consistent interface. The goal
is to  provide an easy set of tools for a software designer to create monitoring
or control applications. There  are some performance enhancements in the
implementation, including data caching, parallel access to bus  masters,
and aggregation of device communication. Still the fundemental goal has
been ease of use, flexibility  and correctness rather than speed.  
\subparagraph*{Ds2423}The
\textsf{\textbf{DS2423 (3)}} is used for its counters. The internal counters (associated with
pages 12 and 13) can detect memory tampering. 

The external counters A and
B page been used in circuit design, such as a wind anometer. \textit{OWFS} system
handles this automatically. 
\paragraph*{Addressing}
          All 1-wire devices are factory
assigned a unique 64-bit address. This address is of the form: \begin{description}
\item [\textbf{Family Code}
] 8 bits 
\item [\textbf{Address} ] 48 bits 
\item [\textbf{CRC} ] 8 bits 
\end{description}


\begin{description}
\item [Addressing under OWFS is in hexidecimal,
of form: ] 
\item [\textbf{01.123456789ABC} ] 
\end{description}


where \textbf{01} is an example 8-bit family code, and \textbf{12345678ABC}
is an example 48 bit address. 

The dot is optional, and the CRC code can
included. If included, it must be correct.  
\paragraph*{Datasheet}


\altlink{http://pdfserv.maxim-ic.com/en/ds/DS2423.pdf} 
\paragraph*{See Also}

\subparagraph*{Programs}\textsf{\textbf{owfs (1)} \textsf{owhttpd
(1)} \textsf{owftpd (1)} \textsf{owserver (1)}} \textsf{\textbf{owdir (1)} \textsf{owread (1)} \textsf{owwrite (1)} \textsf{owpresent
(1)}} \textsf{\textbf{owtap (1)}} 
\subparagraph*{Configuration and testing}\textsf{\textbf{owfs (5)} \textsf{owtap (1)} \textsf{owmon (1)}} 
\subparagraph*{Language
bindings}\textsf{\textbf{owtcl (3)} \textsf{owperl (3)} \textsf{owcapi (3)}} 
\subparagraph*{Clocks}\textsf{\textbf{DS1427 (3)} \textsf{DS1904(3)} \textsf{DS1994
(3)} \textsf{DS2404 (3)} \textsf{DS2404S (3)} \textsf{DS2415 (3)} \textsf{DS2417 (3)}} 
\subparagraph*{ID}\textsf{\textbf{DS2401 (3)} \textsf{DS2411 (3)}
\textsf{DS1990A (3)}} 
\subparagraph*{Memory}\textsf{\textbf{DS1982 (3)} \textsf{DS1985 (3)} \textsf{DS1986 (3)} \textsf{DS1991 (3)} \textsf{DS1992 (3)}
\textsf{DS1993 (3)} \textsf{DS1995 (3)} \textsf{DS1996 (3)} \textsf{DS2430A (3)} \textsf{DS2431 (3)} \textsf{DS2433 (3)} \textsf{DS2502
(3)} \textsf{DS2506 (3)} \textsf{DS28E04 (3)} \textsf{DS28EC20 (3)}} 
\subparagraph*{Switches}\textsf{\textbf{DS2405 (3)} \textsf{DS2406 (3)} \textsf{DS2408
(3)} \textsf{DS2409 (3)} \textsf{DS2413 (3)} \textsf{DS28EA00 (3)}} 
\subparagraph*{Temperature}\textsf{\textbf{DS1822 (3)} \textsf{DS1825 (3)}
\textsf{DS1820 (3)} \textsf{DS18B20 (3)} \textsf{DS18S20 (3)} \textsf{DS1920 (3)} \textsf{DS1921 (3)} \textsf{DS1821 (3)} \textsf{DS28EA00
(3)} \textsf{DS28E04 (3)} \textsf{EDS0064 (3)} \textsf{EDS0065 (3)} \textsf{EDS0066 (3)} \textsf{EDS0067 (3)} \textsf{EDS0068
(3)} \textsf{EDS0071 (3)} \textsf{EDS0072 (3)}} 
\subparagraph*{Humidity}\textsf{\textbf{DS1922 (3)} \textsf{DS2438 (3)} \textsf{EDS0065 (3)} \textsf{EDS0068
(3)}} 
\subparagraph*{Voltage}\textsf{\textbf{DS2450 (3)}} 
\subparagraph*{Resistance}\textsf{\textbf{DS2890 (3)}} 
\subparagraph*{Multifunction (current, voltage,
temperature)}\textsf{\textbf{DS2436 (3)} \textsf{DS2437 (3)} \textsf{DS2438 (3)} \textsf{DS2751 (3)} \textsf{DS2755 (3)} \textsf{DS2756
(3)} \textsf{DS2760 (3)} \textsf{DS2770 (3)} \textsf{DS2780 (3)} \textsf{DS2781 (3)} \textsf{DS2788 (3)} \textsf{DS2784 (3)}} 
\subparagraph*{Counter}\textsf{\textbf{DS2423
(3)}} 
\subparagraph*{LCD Screen}\textsf{\textbf{LCD (3)} \textsf{DS2408 (3)}} 
\subparagraph*{Crypto}\textsf{\textbf{DS1977 (3)}} 
\subparagraph*{Pressure}\textsf{\textbf{DS2406 (3)} -- TAI8570
\textsf{EDS0066 (3)} \textsf{EDS0068 (3)}}  
\paragraph*{Availability}
\altlink{http://www.owfs.org/} 
\paragraph*{Author}
Paul Alfille
(\email{paul.alfille@gmail.com}) 
