% Last Update: $Id$
\paragraph*{Name}
DS2413 - Dual Channel Addressable Switch 
\paragraph*{Synopsis}
Dual Switch


\textbf{3A} [.]XXXXXXXXXXXX[XX][/[ \textbf{PIO.[A$|$B$|$ALL$|$BYTE]} $|$ \textbf{sensed.[A$|$B$|$ALL$|$BYTE]} $|$           \textbf{address}
$|$ \textbf{crc8} $|$ \textbf{id} $|$ \textbf{locator} $|$ \textbf{r\_address} $|$ \textbf{r\_id} $|$ \textbf{r\_locator} $|$ \textbf{type}  ]] 
\paragraph*{Family Code}


\textit{3A}

\paragraph*{Special Properties}

\subparagraph*{Pio.a Pio.b Pio.all Pio.byte}\textit{read-write,} yes-no 

State of the open-drain output ( \textit{PIO} ) pin. 0 = non-conducting (off), 1 =
\textsf{conducting (on)}. 

Writing zero will turn off the switch, non-zero will turn on the switch.
Reading the \textit{PIO} state will return the switch setting. To determine the actual
logic level at the switch, refer to the \textit{sensed} property. 

\textit{ALL} references both channels simultaneously, comma separated. 

\textit{BYTE} references both channels simultaneously as a single byte, with channel
A in bit 0. 
\subparagraph*{sensed.A sensed.B sensed.ALL sensed.BYTE}\textit{read-only,} yes-no 

Logic level at the \textit{PIO} pin. 0 = ground. 1 = high (~2.4V - 5V ). Really makes
sense only if the \textit{PIO} state is set to zero (off), else will read zero. 

\textit{ALL} references both channels simultaneously, comma separated. 

\textit{BYTE} references both channels simultaneously as a single byte, with channel
A in bit 0. 
\paragraph*{Standard Properties}
          
\subparagraph*{address}
\subparagraph*{r\_address}\textit{read-only,} ascii


The entire 64-bit unique ID. Given as upper case hexidecimal digits (0-9A-F).


\textit{address} starts with the \textit{family} code 

\textit{r} address is the \textit{address} in reverse order, which is often used in other
applications and labeling. 
\subparagraph*{crc8}\textit{read-only,} ascii 

The 8-bit error correction portion. Uses cyclic redundancy check. Computed
from the preceding 56 bits of the unique ID number. Given as upper case
hexidecimal digits (0-9A-F). 
\subparagraph*{family}\textit{read-only,} ascii 

The 8-bit family code. Unique to each \textit{type} of device. Given as upper case
hexidecimal digits (0-9A-F). 
\subparagraph*{id}
\subparagraph*{r\_id}\textit{read-only,} ascii 

The 48-bit middle portion of the unique ID number. Does not include the family
code or CRC. Given as upper case hexidecimal digits (0-9A-F). 

\textit{r} id is the \textit{id} in reverse order, which is often used in other applications
and labeling. 
\subparagraph*{locator}
\subparagraph*{r\_locator}\textit{read-only,} ascii 

Uses an extension of the 1-wire design from iButtonLink company that associated
1-wire physical connections with a unique 1-wire code. If the connection is
behind a \textbf{Link Locator} the \textit{locator} will show a unique 8-byte number (16 character
hexidecimal) starting with family code FE. 

If no \textbf{Link Locator} is between the device and the master, the \textit{locator} field
will be all FF. 

\textit{r} locator is the \textit{locator} in reverse order. 
\subparagraph*{present (DEPRECATED)}\textit{read-only,}
yes-no 

Is the device currently \textit{present} on the 1-wire bus? 
\subparagraph*{type}\textit{read-only,} ascii 

Part name assigned by Dallas Semi. E.g. \textit{DS2401} Alternative packaging (iButton
vs chip) will not be distiguished.  
\paragraph*{Alarms}
Use the \textit{set\_alarm} property to
set the alarm triggering criteria. 
\paragraph*{Description}
          
\subparagraph*{1-Wire}\textit{1-wire}  is a
wiring protocol and series of devices designed and manufactured by Dallas
Semiconductor, Inc. The bus is a low-power low-speed low-connector scheme where
the data line can also provide power. 

Each device is uniquely and unalterably
numbered during manufacture. There are a wide variety of devices, including
memory, sensors (humidity, temperature, voltage, contact, current), switches,
timers and data loggers. More complex devices (like thermocouple sensors)
can be built with these basic devices. There are also 1-wire devices that
have encryption included. 

The 1-wire scheme uses a single  \textit{bus} master and
multiple \textit{slaves} on the same wire. The bus master initiates all communication.
The slaves can be  individually discovered and addressed using their unique
ID. 

Bus masters come in a variety of configurations including serial, parallel,
i2c, network or USB adapters. 
\subparagraph*{OWFS design}\textit{OWFS} is a suite of programs that
designed to make the 1-wire bus and its devices easily accessible. The underlying
priciple is to create a virtual filesystem, with the unique ID being the
directory, and the individual properties of the device are represented
as simple files that can be read and written. 

Details of the individual
slave or master design are hidden behind a consistent interface. The goal
is to  provide an easy set of tools for a software designer to create monitoring
or control applications. There  are some performance enhancements in the
implementation, including data caching, parallel access to bus  masters,
and aggregation of device communication. Still the fundemental goal has
been ease of use, flexibility  and correctness rather than speed.  
\subparagraph*{Ds2413}The
\textsf{\textbf{DS2413 (3)}} allows control of other devices, like LEDs and relays. It differs
from the \textit{DS2405} with a cleaner interface and two channels The \textit{DS2413} also
has two channels like the \textit{DS2406} and \textit{DS2407} but has no memory, and no alarm.
There is also varying types of switch and sensing in the \textit{DS2408,} DS2409,
LCD, DS276x, DS2450. 

Unique among the switches, the \textit{DS2413} can switch higher voltages, up to
28V. 
\paragraph*{Addressing}
          All 1-wire devices are factory assigned a unique
64-bit address. This address is of the form: \begin{description}
\item [\textbf{Family Code} ] 8 bits 
\item [\textbf{Address} ] 48
bits 
\item [\textbf{CRC} ] 8 bits 
\end{description}


\begin{description}
\item [Addressing under OWFS is in hexidecimal, of form: ] 
\item [\textbf{01.123456789ABC}
] 
\end{description}


where \textbf{01} is an example 8-bit family code, and \textbf{12345678ABC} is an example
48 bit address. 

The dot is optional, and the CRC code can included. If included,
it must be correct.  
\paragraph*{Datasheet}


\altlink{http://datasheets.maxim-ic.com/en/ds/DS2413.pdf} 
\paragraph*{See Also}

\subparagraph*{Programs}\textsf{\textbf{owfs (1)} \textsf{owhttpd
(1)} \textsf{owftpd (1)} \textsf{owserver (1)}} \textsf{\textbf{owdir (1)} \textsf{owread (1)} \textsf{owwrite (1)} \textsf{owpresent
(1)}} \textsf{\textbf{owtap (1)}} 
\subparagraph*{Configuration and testing}\textsf{\textbf{owfs (5)} \textsf{owtap (1)} \textsf{owmon (1)}} 
\subparagraph*{Language
bindings}\textsf{\textbf{owtcl (3)} \textsf{owperl (3)} \textsf{owcapi (3)}} 
\subparagraph*{Clocks}\textsf{\textbf{DS1427 (3)} \textsf{DS1904(3)} \textsf{DS1994
(3)} \textsf{DS2404 (3)} \textsf{DS2404S (3)} \textsf{DS2415 (3)} \textsf{DS2417 (3)}} 
\subparagraph*{ID}\textsf{\textbf{DS2401 (3)} \textsf{DS2411 (3)}
\textsf{DS1990A (3)}} 
\subparagraph*{Memory}\textsf{\textbf{DS1982 (3)} \textsf{DS1985 (3)} \textsf{DS1986 (3)} \textsf{DS1991 (3)} \textsf{DS1992 (3)}
\textsf{DS1993 (3)} \textsf{DS1995 (3)} \textsf{DS1996 (3)} \textsf{DS2430A (3)} \textsf{DS2431 (3)} \textsf{DS2433 (3)} \textsf{DS2502
(3)} \textsf{DS2506 (3)} \textsf{DS28E04 (3)} \textsf{DS28EC20 (3)}} 
\subparagraph*{Switches}\textsf{\textbf{DS2405 (3)} \textsf{DS2406 (3)} \textsf{DS2408
(3)} \textsf{DS2409 (3)} \textsf{DS2413 (3)} \textsf{DS28EA00 (3)}} 
\subparagraph*{Temperature}\textsf{\textbf{DS1822 (3)} \textsf{DS1825 (3)}
\textsf{DS1820 (3)} \textsf{DS18B20 (3)} \textsf{DS18S20 (3)} \textsf{DS1920 (3)} \textsf{DS1921 (3)} \textsf{DS1821 (3)} \textsf{DS28EA00
(3)} \textsf{DS28E04 (3)} \textsf{EDS0064 (3)} \textsf{EDS0065 (3)} \textsf{EDS0066 (3)} \textsf{EDS0067 (3)} \textsf{EDS0068
(3)} \textsf{EDS0071 (3)} \textsf{EDS0072 (3)}} 
\subparagraph*{Humidity}\textsf{\textbf{DS1922 (3)} \textsf{DS2438 (3)} \textsf{EDS0065 (3)} \textsf{EDS0068
(3)}} 
\subparagraph*{Voltage}\textsf{\textbf{DS2450 (3)}} 
\subparagraph*{Resistance}\textsf{\textbf{DS2890 (3)}} 
\subparagraph*{Multifunction (current, voltage,
temperature)}\textsf{\textbf{DS2436 (3)} \textsf{DS2437 (3)} \textsf{DS2438 (3)} \textsf{DS2751 (3)} \textsf{DS2755 (3)} \textsf{DS2756
(3)} \textsf{DS2760 (3)} \textsf{DS2770 (3)} \textsf{DS2780 (3)} \textsf{DS2781 (3)} \textsf{DS2788 (3)} \textsf{DS2784 (3)}} 
\subparagraph*{Counter}\textsf{\textbf{DS2423
(3)}} 
\subparagraph*{LCD Screen}\textsf{\textbf{LCD (3)} \textsf{DS2408 (3)}} 
\subparagraph*{Crypto}\textsf{\textbf{DS1977 (3)}} 
\subparagraph*{Pressure}\textsf{\textbf{DS2406 (3)} -- TAI8570
\textsf{EDS0066 (3)} \textsf{EDS0068 (3)}}  
\paragraph*{Availability}
\altlink{http://www.owfs.org/} 
\paragraph*{Author}
Paul Alfille
(\email{paul.alfille@gmail.com}) 

